\documentclass[../Bitcoin Blink.tex]{subfiles}
\graphicspath{{\subfix{../assets/images/}}}
\begin{document}
\section{Future}

The future of the Bitcoin network includes building finance-specific L1 applications such as exchanges, bridges, lending \& borrowing, insurance, token minting and bank mirrored wallets. Since these applications are developed inside an unlocking script, it requires preimage construction off-chain and settles onchain - inheriting the security of Bitcoin that centralized applications don't offer. Privacy can be improved by obscuring amounts similar to Monero with tax validation assisting regulators and masking financial information of a specific country. Emphasis on Zk delivery and validation of snips can reduce influence attacks in the future. 

To introduce limitless scalability, an offline digital cash-payment system will be developed with suitable hardware wallets. To provide a general-programmable environment, a State Machine featured with multiple high-level languages using LLVM \cite{llvm} IR code will be deployed as a layer that can update its global \& contract state by providing a gas limit through a receipt-proof paid in Bitcoin Network. The smart-contracts will not contain balances and EOAs, rather purely executed for business-logic to build DApps without a financial scope. To store client-side assets \& data files to build fully decentralized applications, a CDN system will be developed in Bitcoin Network without duplicating data among nodes and provide faster content delivery to end-user. Moreover, research will be conducted to merge various Bitcoin and altcoin chains to a single decentralized global scalable infrastructure for a clean experience on the whole of finance and computing.\\

\noindent Implementations can be contributed openly to \url{https://github.com/projectblink}
\end{document}
