\documentclass[../Bitcoin Blink.tex]{subfiles}
\graphicspath{{\subfix{../assets/images/}}}
\begin{document}

\subsection{Regulation}
Regulation via centralized exchanges \& custodians risks funds and doesn't encourage a self-custodial ecosystem. Regulations are carried out by whitelisting verified hashed public addresses. Regulatory agencies can verify a public address by either doing minimal KYC or something such as mobile number-based OTP verification to encourage privacy through client wallet applications. UTXOs are stamped with region proof on their unlocking script based on specific spending conditions that will only allow a transaction on-chain if taxes are deducted properly. Bitcoin scripts can work efficiently and securely, as opposed to turing-complete smart contracts. 

Tax models such as capital gains slabs can be issued by regulators trustlessly and are validated during the user's script execution. Each Regulator can specify their choice of token/currency from which the market price is derived for the transacted token leading to regulator's choice of market pairs. Confirmed open-order transactions with token swap scripts can provide real-time market price to calculate profitability and impose taxes. Onchain Decentralized Exchange can perform trustless swaps and reduces risk of centralization by price or market-feed oracles from outside sources. External taxes such as TDS and sales tax can be imposed off-chain by wallet-providers with flexibility. These three taxes in a trustless-decentralized way provides almost all the tax models that a regulator can siphon into a centralized payment infrastructure.

\end{document}
