\documentclass[../Bitcoin Blink.tex]{subfiles}
\graphicspath{{\subfix{../assets/images/}}}
\begin{document}
\normalsize
\subsection{Ring Validation}

For each block a set of nodes should validate and attest the VDF proofs to confirm the block, these set of nodes are predictable, assigned and verified. These set of validators of a block is called as ring validators. The name came because a linear structure of elected nodes are treated as a ring to validate a block.

The ring validators should always be unique, finite and its count should be always lesser than the total number of nodes. Each node is treated as equal and can participate in producing blocks in the Bitcoin Network. This eliminates centralization and network halting that's done in popular scalable blockchains.

For VDF Proof attaching, the producer of the block is known as head shall propagate his block in a backward ring manner from n to n+k to n+1, it forms a ring like structure where it ensures that the block with or without intra-block fork shall have the heviest VDF proof block with n+1 block producer.

Since the n+1 producer is the next block producer he will resolve the intra-block forks by updating the heaviest proof of previous block to the following nodes.

When the n+1 producer receives the block, it will propagate to the producer and eliminates him from the ring validation. Such wise, the n+1 producer becomes the head of the ring and the network shall elect a tail of the ring to continue to the propagation of next block's snips. Since tails are newly joined ring validator, upon receiving a snip from the head, it starts its hash-clock, upon triggered. Rest of nodes of ring validators shall continue it hashing upon elected as a tail till it gets eliminated as a head.

When the ring head is eliminated from the ring validator set, it can gossip its confirmed block with heaviest VDF proofs to other nodes connected to the network. Since bandwidth is not consumed for confirmed block propagation, it can be well used to propagate its block for further validation and attaching to all nodes longest chain. 

\end{document}
