\documentclass[../Bitcoin Blink.tex]{subfiles}
\graphicspath{{\subfix{../assets/images/}}}
\begin{document}
\normalsize

\subsection{Election}

\subsubsection{Partcipation}

For every epoch before the allocation of blocks, the joining requirement is increased by eliminating certain nodes' bandwidth proof by conducting a vote with current producers.

\begin{equation*}
|\mathbb{R}| = \{P(B)_1,P(B)_2,...P(B)_n\} 
\end{equation*}
Vote Participants,
\begin{equation*}
\forall |\mathbb{R}| \begin{cases}
|\mathbb{R}| \backslash \{\{P(B)_n\}\} \wedge \in |\mathbb{R}'|, & \text{if } P(B)_n < \bar{x}(|\mathbb{R}|) \\
P(B)_n \in |\mathbb{R}|,  & \text{otherwise}
\end{cases}
\end{equation*}
After Seed,
\begin{equation*}
\forall \mathbb{R'} k = \sum_{P(B)'_n \in |\mathbb{R}|} P(B)'_n
\end{equation*}
\begin{equation*}
\forall \mathbb{R'} \begin{cases}
|\mathbb{R}'| \backslash \{\{P(B)_n\}\}, & \text{ if } k > \bar{x}(|\mathbb{R}|) \cdot (51 \cdot 10^{-2})\\
P(B)_n \in |\mathbb{R}'|, & \text{ otherwise}
\end{cases}
\end{equation*}
Results, 
\begin{equation*}
|\mathbb{R}| = |\mathbb{R}| {\displaystyle \cup } |\mathbb{R}'|, i = \bar{x}(|\mathbb{R}|), |\mathbb{R}|=\emptyset
\end{equation*}
\begin{multicols}{2}
\begin{conditions}
|\mathbb{R}| & Block Producers\\
P(B)_n & PubKey's Bandwidth in bps \\
\bar{x} & Mean value\\
\end{conditions}
\columnbreak
\begin{conditions}
|\mathbb{R}''| & Producers to be voted\\
P(B)'_n & Voted Pubkey's bps\\
i & Joining requirement in bps 
\end{conditions}
\end{multicols}

\subsubsection{Producer Allocation}

Blocks are allocated for a whole epoch from a definite randomized seed where nodes construct the same predictable result. Each producer's bandwidth proof $> i$ will provide the production rate in the number of blocks.

\begin{equation*}
\text{Currently }|\mathbb{R}| = \emptyset, 
\text{If } \epsilon_{(n)}\{P(B)_n...\} > i \in |\mathbb{R}|
\end{equation*}
Block Size/sec,
\begin{equation*}
\epsilon_{n}(j)=min(|\mathbb{R}|) \cdot l
\end{equation*}
Weights addition,
\begin{equation*}
\forall |\mathbb{R}|, P(B)_n = \sum w(P) + P(B)_n = P(w)_n  \in |\mathbb{R}''|
\end{equation*}
Allocation,
\begin{equation*}
\forall |\mathbb{R}''|, \lfloor \Phi_{n} \rfloor = \frac{x \cdot P(w)_n}{10^4 \cdot \sum_{P(w)_n \in |\mathbb{R}''|} P(w)_n} \in |\mathbb{N}|
\end{equation*}
\begin{multicols}{2}
\begin{conditions}
x & No. of blocks per epoch\\
l & Latency\\
w & Individual weights\\
\end{conditions}
\columnbreak
\begin{conditions}
\Phi & Allocated no. of blocks per producer\\
|\mathbb{R}''| & Producers with weight \\
|\mathbb{N}| & Producers with no. of blocks allocation
\end{conditions}
\end{multicols}
\subsubsection{Random Seed}

To randomize the election, between a block range, a seed($k$) - Merkle Chain Root from a confirmed block is found. This seed should lie between a selected range in $2^{256}$ base10 possibilities. The difficulty rate is adjusted every epoch to seed entropy. If a seed is not found, the last block of the range's MCR is taken. 

\begin{equation*}
|\mathbb{S}|= \{1,..2^{256}\} \text{ where, } k \in |\mathbb{S}|
\end{equation*}
\noindent Range Identify,
\begin{equation*}
|\mathbb{F}| = \{[(\frac{p}{d} \cdot q)+h],...(p=2^{256})\} \equiv |\mathbb{S}|
\end{equation*}
\begin{equation*}
h = 0, \text{ } h++ ;\text{ } q = 0, \text{ } q++ \text{ every } \frac{p}{d}
\end{equation*}
Value k,
\begin{equation*}
|\mathbb{X}| = \{[(\frac{p}{d} \cdot q)+h],...[(\frac{p}{d} \cdot q)+h]\}, 
\end{equation*}
\begin{equation*}
\text{ where } q \leq k' \leq q \in |\mathbb{X}|\subset |\mathbb{F}|
\end{equation*}
Difficulty level,
\begin{equation*}
k_{10} \text{ is taken} \begin{cases}
d = 1, k=k' ,     & \text{ if } k' \text{ is } ¿, \exists k \in |\mathbb{X}| \\
d++, k=k' ,       & \text{ if } \exists k \in |\mathbb{X}|\\
d-- \geq 2, k=k', & \text{if } \neg \exists k \in |\mathbb{X}| \vee \exists k \in |\mathbb{F}|\{p\}
\end{cases}
\end{equation*}
%\begin{equation*}
%where k is taken
%\end{equation*}
Block height allocation,
\begin{equation*}
Z_{16} = MD160_{16}((SHA256_{16}(k_{16}+b_h+\epsilon_h))
\end{equation*}
\begin{equation*}
Z_{16}
\begin{cases}
b_h++, P(\Phi_n) \in |\mathbb{L}|, \Phi_n = \Phi_n-1 \in |\mathbb{N}|,   &  \text{ if } |\mathbb{N}| \neq \emptyset \wedge \forall \Phi_n \in |\mathbb{N}| < Z_{16} \\
MD160_{16}(Z_{16}),  & \text{ if } |\mathbb{N}| \neq \emptyset \wedge \forall \Phi_n \in |\mathbb{N}| > Z_{16} \\
|\mathbb{N}| \{\Phi_n\} \backslash  |\mathbb{N}|, & \text{ if } \Phi_n=0\\
\{n(|\mathbb{L}|)+1,..x\}=|\mathbb{L}|\Phi_n =\{1,..\},  & \text{ if } |\mathbb{N}| = \emptyset  \wedge x-n(|\mathbb{L}|)=\mathbb{N}\\
|\mathbb{L}|,   & \text{ if } |\mathbb{N}| = \emptyset \wedge n(|\mathbb{L}|)=x
\end{cases}
\end{equation*}
Block Time,
\begin{equation*}
\epsilon_n b(\tau) = \widetilde{x}(\epsilon_{n-2}(b_1^x)) \in |\mathbb{B}|
\end{equation*}
Block Size,
\begin{equation*}
Block size here (b_s)
\end{equation*}
\begin{conditions}
b_h & Block height in base$_{10}$\\
\epsilon_h & Epoch height in base$_{10}$\\
P(\Phi_n) & Pubkey in MD160 base$_{16}$ rep
\end{conditions}


\end{document}
